The Ontological Modal Collapse \\ as a Collapse of the Square of Opposition

### 2014-09-10 Papers/Universalis/ModalCollapse.tex

All results announced in this note have been 
obtained experimentally using interactive and 
automated theorem provers and model finders
\cite{LEO,Satallax,Isabelle,Coq,Nitpick}.  
The source codes of the experiments, 
as well as the resulting proofs and counter-models, 
are available in
\url{https://github.com/FormalTheology/GoedelGod/tree/master/Formalizations/Isabelle}.
\footnote{C.: Here
  we should point to the exact files (and put them in a relatively
  stable subdirectory?). We also should also use corresponding names in
  these files, so that the reader easily finds the related 
  parst. Right now this is still quite difficult.}

>>>>

All results announced in this note have been 
obtained experimentally using interactive and 
automated theorem provers and model finders
\cite{LEO,Satallax,Isabelle,Coq,Nitpick}.  
The source codes of the experiments, 
as well as the resulting proofs and counter-models, 
are available in
\url{github.com/FormalTheology/GoedelGod/}
in the files \texttt{ModalCollapse.thy} and \texttt{ModalSquareOfOpposition.thy} inside the folder \texttt{Formalizations/Isabelle/Meta} as well as in files inside the folder \texttt{Formalizations/Isabelle/Anderson}.
